Closer look at DDM parameter estimates

### 2017-06-05 DDM_Report.Rmd
cont working on ddm report
adding uncommitted changes to the ddm report

**GO ON SHERLOCK AND CHECK IF YOU INDEED FIT IT TO THE RETEST SAMPLE ONLY**

@@

```{r}
raw_retest_data <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/raw_retest_data.csv')
```

>>>>

@@

```{r}
all_ddm_sample_size <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/all_ddm_sample_size_estimates.csv')

all_ddm_sample_size  = all_ddm_sample_size %>%
  drop_na()
```
